---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Your cli pal

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/clipal)](https://CRAN.R-project.org/package=clipal)
<!-- badges: end -->

A couple years ago, the tidyverse team began migrating to the cli R package for raising errors, transitioning away from base R (e.g. `stop()`), rlang (e.g. `rlang::abort()`), glue, and homegrown combinations of them. cli's new syntax is easier to work with as a developer and more visually pleasing as a user.

In some cases, transitioning is as simple as Finding + Replacing `rlang::abort()` to `cli::cli_abort()`. In others, there's a mess of ah-hoc pluralization, `paste0()`s, glue interpolations, and other assorted nonsense to sort through. Total pain, especially with thousands upon thousands of error messages thrown across the tidyverse, r-lib, and tidymodels organizations.

clipal ("c-l-i pal") is an RStudio add-in that helps you convert your R package to use cli for error messages. It's vaguely correct most of the time, and greatly speeds up the process for converting error messages to cli, in my experience.

## Installation

You can install the development version of clipal like so:

``` r
pak::pak("simonpcouch/clipal")
```

## Example

The `cli_pal()` function instantiates a cli pal (a light wrapper around an elmer chat).

```{r}
library(clipal)

cli_pal <- cli_pal()
```

The `convert_to_cli()` function takes an R expression that raises a condition and converts it to use cli. At its simplest:

```{r}
convert_to_cli(stop("An error message."), cli_pal)
```

The function can handle surprisingly complex erroring code, though:

```{r}
convert_to_cli(
  {
    types <- paste0(pred_types, collapse = ", ")
    rlang::abort(
      glue::glue(
        "The model only has prediction types {types}. Did you ",
        "fit the model with `silly_head = TRUE`?"
      )
    )
  },
  cli_pal
)
```








TODO: show by function, file, and package...



